Plots_GAM

### 2024-05-23 Code/Plots_GAM.Rmd
Cleaned code

@@

```{r, MED4PAR, fig.height=10, fig.width=10}
MyWavelengths = c("WW", 660, 450)

@@

MED4PAR <- GrowthFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          WL %in% c("WW", 450, 660),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~concentration~(µM)",
         WLlabelTitle = "Growth~wavelength~(nm)",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(WL, levels = c("WW", 660, 530, 450)),
         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
  ggplot()  +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
 labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
       strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 16),  #change legend title font size
        legend.text = element_text(size = 12),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth wavelength (nm)",
       fill = "Growth wavelength (nm)")
MED4PAR

@@

``` {r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
GamStrain = "MED4" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"
data_text <- data.frame(label = c('450 nm, 250 µM'))
# data_textB <- data.frame(label = c('B'))

@@

minMu <- PicoGAM_Pred %>%
  ungroup() %>%
  filter(Wavelength %in% PlotWL) %>%
  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
  #        fit == min(fit, na.rm = TRUE)) %>%
  # distinct(fit)
minMu <- minMu$fit

@@

(ContourMED4BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.y = element_blank(),
         # axis.title.y = element_text(margin=margin(r=10)),
         axis.title.x = element_blank(),
        # axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

@@

(ContourMED4BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         # axis.title.y = element_text(margin=margin(r=10)),
         axis.title.y = element_blank(),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

@@

(ContourMED4RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
  # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         # axis.title.y = element_text(margin=margin(r=10)),
         axis.title.x = element_blank(),
        # axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

@@

(ContourMED4RedInt <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         # axis.title.y = element_text(margin=margin(r=10)),
        # axis.title.y = element_blank(),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

@@

@@

```{r save MED4PARGAM plots}
# MED4GAM,png for manuscript
 ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MED4PARGAM,  height = 15, width = 10)

# MED4GAM is Fig4.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")

@@

```{r, SS120PAR, fig.height=10, fig.width=10}
MyWavelengths = c("WW", 660, 450)

@@

SS120PAR <- GrowthFits %>%
   filter(Strain == "SS120",
           Par_ue %in% c(30,90,180),
          WL %in% c("WW", 450, 660),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~concentration~(µM)",
         WLlabelTitle = "Growth~wavelength~(nm)",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(WL, levels = c("WW", 660, 530, 450)),
         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
  ggplot()  +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
 labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
       strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 16),  #change legend title font size
        legend.text = element_text(size = 12),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth wavelength (nm)",
       fill = "Growth wavelength (nm)")
SS120PAR

@@

``` {r SS120GAM Plot Blue WL 250, fig.height=5, fig.width=5}
GamStrain = "SS120" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"
data_text <- data.frame(label = c('450 nm, 250 µM'))
# data_textB <- data.frame(label = c('B'))

@@

(ContourSS120BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.y = element_blank(),
         # axis.title.y = element_text(margin=margin(r=10)),
         axis.title.x = element_blank(),
        # axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

@@

>>>>

```{r, set colors for wavelength}

MyWavelengths = c("WW", 660, 450)

@@

```{r, MED4PAR, fig.height=10, fig.width=10}

@@

MED4PAR <- GrowthFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          WL %in% c("WW", 450, 660),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~concentration~(µM)",
         WLlabelTitle = "Growth~wavelength~(nm)",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         WL = factor(WL, levels = c("WW", 660, 530, 450)),
         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
  ggplot()  +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
 labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
       strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 16),  #change legend title font size
        legend.text = element_text(size = 12),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth wavelength (nm)",
       fill = "Growth wavelength (nm)")
MED4PAR

@@

``` {r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
GamStrain = "MED4" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"
data_text <- data.frame(label = c('450 nm, 250 µM'))

@@

@@

(ContourMED4BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.y = element_blank(),
         axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
```

@@

(ContourMED4BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.y = element_blank(),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)

@@

(ContourMED4RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)

@@

(ContourMED4RedInt <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)

@@

remove(MED4PAR, ContourMED4RedHigh, ContourMED4BlueHigh, ContourMED4RedInt, ContourMED4BlueInt)

@@

```{r save MED4PARGAM plots}
# MED4PARGAM.png for manuscript
 ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MED4PARGAM,  height = 15, width = 10)

# MED4PARGAM is Fig4.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")

@@

```{r, SS120PAR, fig.height=10, fig.width=10}

@@

SS120PAR <- GrowthFits %>%
   filter(Strain == "SS120",
           Par_ue %in% c(30,90,180),
          WL %in% c("WW", 450, 660),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~concentration~(µM)",
         WLlabelTitle = "Growth~wavelength~(nm)",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         WL = factor(WL, levels = c("WW", 660, 530, 450)),
         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
  ggplot()  +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
 labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
       strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
      # legend.title = element_text(size = 15), #change legend title font size for right side legend placement
      # legend.text = element_text(size = 15),  #change legend text font size for right side legend placement
        legend.title = element_text(size = 16),  #change legend title font size
        legend.text = element_text(size = 12),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth wavelength (nm)",
       fill = "Growth wavelength (nm)")
SS120PAR

@@

``` {r SS120GAM Plot Blue WL 250, fig.height=5, fig.width=5}
GamStrain = "SS120" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"
data_text <- data.frame(label = c('450 nm, 250 µM'))

@@

(ContourSS120BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 205)) +
    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.y = element_blank(),
         axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)

@@

remove(SS120PAR, ContourSS120RedHigh, ContourSS120BlueHigh, ContourSS120RedInt, ContourSS120BlueInt)
